\chapter{Conclusion}
\label{chp:conclusion}

\section{Conclusion}
With the results the experiments have yielded, seen in chapter \ref{chp:results}, does it looks like machine learning is a good way of detecting \gls{dns} tunnels. The classifier model \gls{ocsvm} with the default kernel \texttt{rbf}, does create a good decision function which the graphs shows. The table \ref{tab:predicting} shows that the predicting function also gives good results. Even though it is not possible to say if it is completely correct. The dataset is unlabeled and might not contain a \gls{dns} tunnel, but the results gives indication of sessions and users which should be inspected. The Elliptical envelope model has the disadvantage that it has to create a ellipse as the decision function which seems to make inaccurate either making the decision function cover a very large or too small area. As seen in \ref{fig:scaledUpDownDivDur} mot the Robust Covariance and the Empirical Covariance cover smaller area of observations and larger area of blank space than the \gls{ocsvm}. The linear kernel of \gls{ocsvm} finds a linear function in which observation on one side is the inliers and the other side is the outliers. This showed some results with some of the features, but was worse than the rbf kernel overall.


\section{Future work}
With the findings in this project could it be interesting doing experiments where with data know to contain a \gls{dns} tunnel, either continue with unlabeled learning or label the data and to supervised learning. This could also be tested against one another. Also creating a program which could take in a real time data stream and give out suspicious connection based on this model or the best model from the previous experiment mentioned, making it a complete program for tunnel detection. There are also more to data to look at to make a complete detection program. The dataset contained also had information about other services the user did. Combining more features might be of help, e.g. look if an user makes a \texttt{http} request after the \gls{dns} session or what kind of data plan the user has. 